\textit{Complex Variables and Elliptic Equations} \LaTeX\ guide for authors (Style 2 + NLM reference style)

### 2016-12-21 cvee_paper_gerasimovd.tex
CVEE template

\newcommand{\mcO}{\mathcal{O}} % Big O
\newcommand{\iu}{{i\mkern1mu}} % imaginary unit
\newcommand{\eexp}[1]{e^{#1}}  % convenient exponent

\renewcommand{\Re}{\operatorname{Re}} % default Re/Im is weird
\renewcommand{\Im}{\operatorname{Im}}

% \DeclarePairedDelimiter\abs{\lvert}{\rvert}%
% \DeclarePairedDelimiter\norm{\lVert}{\rVert}%

\newcommand\abs[1]{\left|#1\right|}
\DeclareMathOperator\asin{asin}
\DeclareMathOperator\atanh{atanh}
\begin{document}

@@

% In order to assist authors in the process of preparing a manuscript for \textit{Complex Variables and Elliptic Equations} (\textit{gCOV}), the journal's layout style has been implemented as a \LaTeXe\ class file based on the \texttt{article} document class. A \textsc{Bib}\TeX\ style file is also provided to assist with the formatting of your references in a style appropriate to that of the journal.

% Commands that differ from or are provided in addition to the standard \LaTeXe\ interface are explained in this guide. The guide alone is not intended as a substitute for an appropriate \LaTeXe\ manual.

% The \texttt{gCOVguide.tex} file can also be used as a template for composing an article for submission by cutting, pasting, inserting and
% deleting text as appropriate, using the \LaTeX\ environments provided (e.g. \verb"\begin{equation}", \verb"\begin{enumerate}").

% \textbf{Please note that the index following the abstract in this guide is provided for information only. An index is not required in submitted papers.}

@@

\begin{theorem}[{\cite[p. 95]{nikol2012treatise}}, {\cite[p. 99]{nikol2012treatise}}]
The following statements are equivalent:
\begin{itemize}
\item the dissipating operator $Z$ is complete
\item
\begin{equation}\label{eq:blaschke}
\lim\limits_{r = 1} \int\limits_{\mathbb{T}} \log \abs{\det S(r \zeta)} d m(\zeta) = 0
\end{equation}
\end{itemize}
\end{theorem}

@@

\section{Proof of completeness of resonant states}

\section{Using the \textit{gCOV} class file}

If the file \texttt{gCOV2e.cls} is not already in the appropriate system directory for \LaTeXe\ files, either
arrange for it to be put there, or simply copy it to your working folder. In order to use the \textit{gCOV} document class, replace the command
\verb"\documentclass{article}" at the beginning of your document with the command \verb"\documentclass{gCOV2e}".

The following document-class options should \emph{not} be used with the \textit{gCOV} class file:
\begin{itemize}
  \item \texttt{10pt}, \texttt{11pt}, \texttt{12pt} -- unavailable;
  \item \texttt{oneside}, \texttt{twoside} -- not necessary, oneside is the default;
  \item \texttt{leqno}, \texttt{titlepage} -- should not be used;
  \item \texttt{onecolumn} -- not necessary as it is the default style.
\end{itemize}
The \texttt{geometry} package and commands associated with it should also not be used to adjust the page dimensions.

\section{Additional features}

\subsection{Title, authors' names, abstract and keywords}

The title should be generated at the beginning of your article using the \verb"\maketitle" command.
In the final version, the author name(s) and affiliation(s) must be followed immediately by \verb"\maketitle" as shown below in order for them to be displayed in your PDF document.
To prepare an anonymous version for peer review, you can put the \verb"\maketitle" between the \verb"\title" and the \verb"\author" in order to conceal the authors' identities from the reviewers.
Next you should include an abstract, which should be enclosed within an \texttt{abstract} environment.
For example, the titles for this guide begin as follows:
\begin{verbatim}
\title{\textit{Complex Variables and Elliptic Equations} \LaTeX\
guide for authors (Style 2 + NLM reference style)}

\begin{abstract}
This guide is for authors who are preparing papers for \textit{Complex
Variables and Elliptic Equations} (\textit{gCOV}) using the \LaTeX\
document preparation system and the class file \texttt{gCOV2e.cls},
which is available via the journal's home page on the Taylor \&
Francis website.
\end{abstract}
\end{verbatim}
A list of keywords should follow the abstract, enclosed within a \texttt{keywords} environment, followed by subject classification codes enclosed within a \texttt{classcode} environment.

\subsection{Additional footnotes to the title or authors' names}

The \verb"\thanks" command may be used to produce additional footnotes to the title or authors' names if required.
Footnote symbols for this purpose should be used in the order:
$\dagger$ (coded as \verb"\dagger"), $\ddagger$ (\verb"\ddagger"), $\S$ (\verb"\S"), $\P$ (\verb"\P"), $\|$ (\verb"\|"),\break
$\dagger\dagger$ (\verb"\dagger\dagger"), $\ddagger\ddagger$ (\verb"\ddagger\ddagger"), $\S\S$ (\verb"\S\S"),
$\P\P$ (\verb"\P\P"), $\|\|$ (\verb"\|\|").

Note that any \verb"footnote"s to the main text will automatically be assigned the superscript
 symbols 1, 2, 3, etc. by the class file.\footnote{If preferred, the \texttt{endnotes} package
 may be used to set the notes at the end of your text, before the bibliography.
 The symbols will be changed to match the style of the journal if necessary by the typesetter.}

\subsection{Lists}

The \textit{gCOV} class file provides numbered and unnumbered lists using the \texttt{enumerate} environment and bulleted
lists using the \texttt{itemize} environment.

The enumerated list will number each list item with arabic numerals by default. For example,
\begin{enumerate}
  \item first item
  \item second item
  \item third item
\end{enumerate}
was produced by
\begin{verbatim}
\begin{enumerate}
  \item first item
  \item second item
  \item third item
\end{enumerate}
\end{verbatim}
Alternative numbering styles can be achieved by inserting an optional argument in square brackets to each \verb"item", e.g. \verb"\item[(i)] first item"\, to create a list numbered with roman numerals.

Unnumbered lists can also be produced using the \texttt{enumerate} environment, e.g.
\begin{enumerate}
  \item[] First unnumbered item
  \item[] Second unnumbered item
  \item[] Third unnumbered item
\end{enumerate}
was produced by
\begin{verbatim}
\begin{enumerate}
  \item[] First unnumbered item
  \item[] Second unnumbered item
  \item[] Third unnumbered item
\end{enumerate}
\end{verbatim}

Bulleted lists are provided using the \texttt{itemize} environment. For example,
\begin{itemize}
  \item First bulleted item
  \item Second bulleted item
  \item Third bulleted item
\end{itemize}
was produced by
\begin{verbatim}
\begin{itemize}
  \item First bulleted item
  \item Second bulleted item
  \item Third bulleted item
\end{itemize}
\end{verbatim}

\section{Some guidelines for using standard features}

The following notes are intended to help you achieve the best effects with the \texttt{gCOV2e} class file.

\subsection{Sections}

\LaTeXe\ provides five levels of section heading, all of which are defined in the \texttt{gCOV2e} class file:
\begin{enumerate}
  \item[(A)] \verb"\section"
  \item[(B)] \verb"\subsection"
  \item[(C)] \verb"\subsubsection"
  \item[(D)] \verb"\paragraph"
  \item[(E)] \verb"\subparagraph"
\end{enumerate}
Section, subsection, subsubsection and paragraph headings are numbered automatically.
If you need additional text styles in the headings, see the examples given in Section~\ref{headings}.

\subsection{Illustrations (figures)}

See `Instructions for Authors' in the journal's home page on the Taylor \& Francis website for how to submit artwork (note that requests to supply figures and tables separately from text are for the benefit of authors using Microsoft Word; authors using \LaTeX\ may incorporate these at the appropriate locations). The source files of any illustrations will be required when the final, revised version is submitted. Authors should ensure that their figures are suitable (in terms of lettering size, etc.) for the reductions they intend.

The \textit{gCOV} class file will cope with most positioning of your illustrations and you should not normally need to use the optional placement specifiers of the \texttt{figure} environment.
Figure captions should appear below the figure itself, therefore the \verb"\caption" command should appear after the figure.
For example, Figure~\ref{sample-figure} with caption and sub-captions is produced using the following commands:
\begin{verbatim}
\begin{figure}
\begin{center}
\subfigure[An example of an individual figure sub-caption.]{
\resizebox*{5cm}{!}{\includegraphics{senu_gr1.eps}}}\hspace{5pt}
\subfigure[A slightly shorter sub-caption.]{
\resizebox*{5cm}{!}{\includegraphics{senu_gr2.eps}}}
\caption{Example of a two-part figure with individual sub-captions
 showing that captions are flush left and justified if greater
 than one line of text, otherwise centred below the figure.}
\label{sample-figure}
\end{center}
\end{figure}
\end{verbatim}

\begin{figure}
\begin{center}
\subfigure[An example of an individual figure sub-caption.]{
\resizebox*{5cm}{!}{\includegraphics{senu_gr1.eps}}}\hspace{5pt}
\subfigure[A slightly shorter sub-caption.]{
\resizebox*{5cm}{!}{\includegraphics{senu_gr2.eps}}}
\caption{Example of a two-part figure with individual sub-captions
 showing that captions are flush left and justified if greater
 than one line of text, otherwise centred below the figure.}
\label{sample-figure}
\end{center}
\end{figure}

The \verb"\subfigure{}" and \verb"\includegraphics{}" commands require subfigure.sty and graphicx.sty.
The former is called in the preamble of the \texttt{gCOVguide.tex} file (in order to allow your choice of an alternative package if preferred)
and the latter by the \texttt{gCOV2e} class file; both are included with the \LaTeX\ style guide package for this journal for convenience.
Please supply any additional figure macros you use with your article in the preamble of your .tex file before \verb"\begin{document}".

To ensure that figures are correctly numbered automatically, the \verb"\label{}" command should be inserted just
after the \verb"\caption{}" command, or in its argument.

The \texttt{epstopdf} package can be used to incorporate Encapsulated PostScript (.eps) illustrations when using PDF\LaTeX, etc.
Please provide the original .eps source files rather than the generated PDF images of those illustrations for production purposes.

\subsection{Tables}

The \textit{gCOV} class file will cope with most positioning of your tables and you should not normally need to use the optional
placement specifiers of the \texttt{table} environment.

The \texttt{tabular} environment can be used as illustrated here to produce tables with appropriately spaced single thick and thin
horizontal rules, which are allowed, if desired. Thick rules should be used at the head and foot only, and thin rules elsewhere as appropriate.
Commands to redefine quantities such as \verb"\arraystretch" should be omitted.

The table caption appears above the body of the table in \textit{gCOV} style, therefore the \verb"\tbl" command should be used before the body of the table.
For example, Table~\ref{sample-table} is produced using the following commands. Note that \verb"\rm" will produce a roman character in math mode.
There are also \verb"\bf" and \verb"\it", which produce bold face and text italic in math mode.

\begin{table}
\tbl{Example of a table showing that its caption is as wide as the
 table itself and justified.}
{\begin{tabular}[l]{@{}lcccccc}\toprule
  Class$^{\rm a}$ & $\gamma _1$ & $\gamma _2$$^{\rm b}$
         & $\langle \gamma \rangle$
         & $G$ & $|{\bm f}|$ & $\theta _{c}$ \\
\colrule
  BL Lacs & 5 & 36 & 7 & $-4.0$ & $1.0\times 10^{-2}$ & 10$^\circ$ \\
  FSRQs & 5 & 40 & 11 & $-2.3$ & $0.5\times 10^{-2}$ & 14$^\circ$ \\
\botrule
\end{tabular}}
\tabnote{$^{\rm a}$This footnote shows what footnote symbols to use.}
\tabnote{$^{\rm b}$This footnote shows the text turning over when a long footnote is added.}
\label{sample-table}
\end{table}

\begin{verbatim}
\begin{table}
\tbl{Example of a table showing that its caption is as wide as the
 table itself and justified.}
{\begin{tabular}[l]{@{}lcccccc}\toprule
  Class$^{\rm a}$ & $\gamma _1$ & $\gamma _2$$^{\rm b}$
         & $\langle \gamma \rangle$
         & $G$ & $|{\bm f}|$ & $\theta _{c}$ \\
\colrule
  BL Lacs & 5 & 36 & 7 & $-4.0$ & $1.0\times 10^{-2}$ & 10$^\circ$ \\
  FSRQs & 5 & 40 & 11 & $-2.3$ & $0.5\times 10^{-2}$ & 14$^\circ$ \\
\botrule
\end{tabular}}
\tabnote{$^{\rm a}$This footnote shows what footnote symbols to use.}
\tabnote{$^{\rm b}$This footnote shows the text turning over when a
 long footnote is added.}
\label{sample-table}
\end{table}
\end{verbatim}

To ensure that tables are correctly numbered automatically, the \verb"\label{}" command should be inserted just before \verb"\end{table}".

Tables produced using the \texttt{booktabs} package of macros for typesetting tables are also compatible with the \textit{gCOV} class file.

\subsection{Landscape pages}\label{landscape}

If a table or illustration is too wide to fit the measure it will need to be turned, along with its caption, through 90$^{\circ}$ anticlockwise.
Landscape illustrations and/or tables can be produced using the \verb"rotating" package, which is called by the \textit{gCOV} class file.
The following commands (for example) can be used to produce such pages.
\begin{verbatim}
\setcounter{figure}{0}
\begin{sidewaysfigure}
\centerline{\epsfbox{figname.eps}}
\caption{Example landscape figure caption.}
\label{landfig}
\end{sidewaysfigure}
\end{verbatim}

\begin{verbatim}
\setcounter{table}{0}
\begin{sidewaystable}
 \tbl{Example landscape table caption.}
  {\begin{tabular}{@{}llllcll}
    .
    .
    .
  \end{tabular}}\label{landtab}
\end{sidewaystable}
\end{verbatim}
Before any such float environment, use the \verb"\setcounter" command as above to fix the numbering of the caption.
Subsequent captions will then be automatically renumbered accordingly.
The \verb"\epsfbox{}" command requires epsfig.sty, which is called by the \texttt{gCOV2e} class file and included with the \LaTeX\ style guide package for this journal for convenience.

\subsection{Theorem-like environments}

A predefined \verb"proof" environment is provided by the \texttt{amsthm} package (which is called by the \textit{gCOV} class file), as follows:

\begin{proof}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{proof}
\noindent This was produced by simply typing:
\begin{verbatim}
\begin{proof}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{proof}
\end{verbatim}
Other theorem-like environments (theorem, lemma, corollary, etc.) need to be defined as required, e.g. using \verb"\newtheorem{theorem}{Theorem}[section]"
in the preamble of your .tex file before \verb"\begin{document}". Theorem-like structures in \textit{gCOV} are generally numbered as per the following examples:

\begin{theorem}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{theorem}
\begin{lemma}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{lemma}
\begin{corollary}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{corollary}
\begin{proposition}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{proposition}
\begin{definition}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{definition}
\begin{remark}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{remark}

\noindent These were defined as shown in detail in the preamble of the \texttt{gCOVguide.tex} file, and produced by typing, for example:
\begin{verbatim}
\begin{theorem}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{theorem}
\end{verbatim}
The format of the text in these environments may be changed if necessary to match the style of the journal by the typesetter during preparation of your proofs.

\subsection{Typesetting mathematics}\label{maths}

\subsubsection{Displayed mathematics}

The \textit{gCOV} class file will set displayed mathematics centred on the measure without equation numbers if the \LaTeX\ standard commands open (\verb"\[") and close (\verb"\]") square brackets are used as
delimiters. The equation
\[
  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})\qquad
  i\in {\mathbb R}
\]
\normalfont was typeset using the commands
\begin{verbatim}
\[
  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})\qquad
  i\in {\mathbb R}
\]
\end{verbatim}

For those of your equations that you wish to be automatically numbered sequentially throughout the text,
use the \texttt{equation} environment, e.g.
\begin{equation}
  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})\qquad
  i\in {\mathbb R}
\end{equation}
was typeset using the commands
\begin{verbatim}
\begin{equation}
  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})quad
  i\in {\mathbb R}
\end{equation}
\end{verbatim}

Part numbers for sets of equations may be generated using the \texttt{subequations} environment, e.g.
\begin{subequations} \label{subeqnexample}
\begin{equation}
        \varepsilon \rho w_{tt}(s,t)
        =
        N[w_{s}(s,t),w_{st}(s,t)]_{s},
        \label{subeqnpart}
\end{equation}
\begin{equation}
        w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,
\end{equation}
\end{subequations}
which was generated using the commands
\begin{verbatim}
\begin{subequations} \label{subeqnexample}
\begin{equation}
        \varepsilon \rho w_{tt}(s,t)
        =
        N[w_{s}(s,t),w_{st}(s,t)]_{s},
        \label{subeqnpart}
\end{equation}
\begin{equation}
        w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,
\end{equation}
\end{subequations}
\end{verbatim}
This is made possible by the \texttt{subeqn} package, which is called
by the class file. If you put the \verb"\label{}" just after the
\verb"\begin{subequations}" line, references will be to the
collection of equations, `(\ref{subeqnexample})' in the example
above. Or, like the example code above, you can reference each
equation individually -- e.g. `(\ref{subeqnpart})'.

>>>>

\newcommand{\mcO}{\mathcal{O}} % Big O
\newcommand{\iu}{{i\mkern1mu}} % imaginary unit
\newcommand{\eexp}[1]{e^{#1}}  % convenient exponent
\renewcommand{\Re}{\operatorname{Re}} % default Re/Im is weird
\renewcommand{\Im}{\operatorname{Im}}
\newcommand\abs[1]{\left|#1\right|}
\newcommand\norm[1]{\left\|#1\right\|}
\DeclareMathOperator\asin{asin}
\DeclareMathOperator\atanh{atanh}
\begin{document}

@@

@@

\begin{theorem}[{\cite[p. 95, 99]{nikol2012treatise}}]
The following statements are equivalent:
\begin{itemize}
\item the dissipating operator $Z$ is complete
\item
\begin{equation}\label{eq:blaschke}
\lim\limits_{r = 1} \int\limits_{\mathbb{T}} \log \abs{\det S(r \zeta)} d m(\zeta) = 0
\end{equation}
\end{itemize}
\end{theorem}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[trim=0 670 155 0,clip,width=\textwidth]{resonator_bundle.eps}
\caption{Quantum graph $\Gamma$, consisting of semi infinite edges $\Omega_L, \Omega_R$ 
and a resonator $\Omega$, consisting of $W$ identical edges of length 1.}
\label{fig:res_bundle}
\end{center}
\end{figure}

Let's investigate the model on Figure~\ref{fig:res_bundle}. Schrodinger's operator is defined on the edges of the graph as  $-\frac{d^2 \psi}{dx^2}$. At the vertices $V_a$ and $V_b$ we require the wavefunction and its derivatives to be continuous:

\begin{equation}\label{eq:bundle_system}
\begin{aligned}
   \forall i: \psi_i(0) &= \psi_L(0)
\\ \forall i: \psi_i(1) &= \psi_R(0)
\\ \psi'_L(0) - \sum\limits_{i = 1}^W \psi'_i(0) &= 0
\\ -\psi'_R(0) + \sum\limits_{i = 1}^W \psi'_i(1) &= 0
\end{aligned}
\end{equation}

After solving (\ref{eq:bundle_system}) in conjunction with (\ref{eq:wlwl}), we get:
\begin{equation*}
\det S(k) = \frac{2 i \, W \cos\left(k\right) - {\left(W^{2} + 1\right)} \sin\left(k\right)}{2 i \, W \cos\left(k\right) + {\left(W^{2} + 1\right)} \sin\left(k\right)}
\end{equation*}

\section{Proof of completeness of resonant states}
Using the S-matrix obtained above, we get:

\begin{equation}\label{eq:bundle_s}
s(k) = \abs{\det S(k)} = \abs{\frac{2 i \, W \cos\left(k\right) - {\left(W^{2} + 1\right)} \sin\left(k\right)}{2 i \, W \cos\left(k\right) + {\left(W^{2} + 1\right)} \sin\left(k\right)}}
\end{equation}

To prove completeness, we have to show that the criterion (\ref{eq:critp}) holds for this function. We will treat the integral as a function of $R$ and give it an upper bound such that it vanishes as $r \to 1$ and $R \to \infty$, which means that the integral vanishes as well, hence the completeness of resonant states.

Now, let's fix $r$, and further, for the sake of readability, we define $C = C(r)$ and $R = R(r)$.

To estimate, we need the Cauchy-Schwarz's inequality:
\[
\big| \langle u,v \rangle \big| \leq \left\|u\right\| \left\|v\right\|
\]
, or to be precise, it's $\mathcal{L}^2[a, b]$ version:
\[
\abs{
\int\limits_{t=a}^{b} f(t) g^*(t) dt
}
\le
\sqrt{\int\limits_{t=a}^b \abs{f(t)}^2 dt }
\sqrt{\int\limits_{t=a}^b \abs{g(t)}^2 dt }
\]
% 
To use inequality, we are going to represent the integrand in (\ref{eq:critp}) as $f(t) g^*(t)$ as follows:
\begin{equation}\label{eq:split}
\begin{aligned}
a      &= 0 \\
b      &= 2 \pi \\
f(t)   &= \ln s(R \eexp{\iu t} + \iu C) \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i} \\
g^*(t) &= \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i}
\end{aligned}
\end{equation}
Next, we will show that $\norm{g}$ (that is, $\sqrt{\int \abs{g(t)}^2}$) is bounded by a constant which does not depend on $r$, and $\norm{f}$ goes to $0$ as $r$ goes to $1$, hence (\ref{eq:critp}) converges.

\subsection{Estimating $\norm{g}$}

First, we evaluate the integrand:
\begin{align*}
\abs{g(t)}^2 = \abs{g^*(t)}^2
&=   \frac{\sqrt{R}^2}{\abs{R \cos t + \iu R \sin t + \iu C + i}^2} \\
&=   \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} \\
&= \frac{R}{R^2 \cos^2 t + R^2 \sin^2 t + (C + 1)^2  + 2 R (C + 1) \sin t} \\
&=   \frac{1}{R + \frac{(C + 1)^2}{R} + 2 (C + 1) \sin t} \\ 
\end{align*}

We have to integrate this function on interval $[0, 2 \pi]$. Integral of such type is well-known: % REFTODO
\[
\int\limits_{0}^{2 \pi} \frac{dx}{a + b \sin x} = \frac{2 \pi}{\sqrt{a^2 - b^2}}
\]
, when $a > b$. In our case, $a = R + \frac{(C + 1)^2}{R}$, $b = 2 (C + 1)$).

First, we check that $a > b$:
\begin{align*}
   R + \frac{(C + 1)^2}{R} - 2 (C + 1)
   &= \frac{R^2 + C^2 + 2C + 1 - 2 RC - 2 R}{R}
\\ &= \frac{(C - R)^2 + 2(C - R) + 1}{R}
\\ &= \frac{(C - R + 1)^2 }{R}
\\ &> 0 && \text{,strictly greater since $C > R$} 
\end{align*}

Next, we compute en estimate for $\sqrt{a^2 - b^2}$:
\begin{align*}
a^2 - b^2
& =  (R + \frac{(C + 1)^2}{R})^2 - (2 (C + 1))^2\\
& =  R^2 + \frac{(C+1)^4}{R^2} + 2 (C+1)^2 - 4 (C + 1)^2 \\
& =  \left( \frac{(C + 1)^2}{R} - R \right)^2 \\
& =  \left( \frac{(C + 1)^2 - R^2}{R}\right)^2 \\
& =  \left( \frac{(C + 1 - R) (C + 1 + R)}{R}\right)^2 && \text{,since $C > R > 0$} \\
&\ge \left( \frac{(1) (R + R)}{R}\right)^2  \\
&\ge 4
\end{align*}

Finally, since $\frac{2 \pi}{\sqrt{a^2 - b^2}} \le \frac{2 \pi}{2} = \pi$, and we just proved that $\norm{g}$ is bounded by a constant.

\subsection{Estimating $\norm{f}$}
Function $s(k)$ (\ref{eq:bundle_s}) is too complex for direct proof of the convergence.

We proceed as follows:

\begin{itemize}
\item Since $s(k)$ is an absolute value of the determinant of the $S$ matrix, in the upper complex plane $0 \le s(k) \le 1$ holds. From here, we immediately know that the integral is bounded from above since $ln^2 1 = 0$.
\item We replace $s(k)$ with a lower bound $l(k)$ such that: $0 \le l(k) \le s(k) \le 1$.
\item By appling logarithm to the expression above, we get $\ln l(k) \le \ln s(k) \le 0$, and therefore, $\ln^2 s(k) \le \ln^2 l(k)$.
\item Now, if we prove convergence for $l(k)$, this immediately proves the convergence of the original integral.
\end{itemize}

We are going to use this fact in our proof and do such function changes under the integral sign, replacing complicated function with simpler (in particular, piecewise linear) lower bounds, and then using well known facts to estimate the integral.

\subsubsection{Simplifying $s(k)$}
We build a simple estimate for $s(k)$ over the upper complex plane. This function will be independent of the complex part of its argument which will make the analysis way easier.

\begin{enumerate}
\item
  It is easy to spot that if we fix the complex part of the argument, $s(k)$ is periodic with respect to the real part of its argument.
\item 
  Function $s(k)$ has countably infinite set of zeros, and each of them has $\Im k = \atanh \frac{2 W}{W^2 + 1}$. For brewity, we define:

  \begin{equation*}
  \begin{aligned}
     V &= \frac{2 W}{W^2 + 1}
  \\ Z &= \atanh V
  \end{aligned}
  \end{equation*}
\item
  Notice that for each $x$, $s(x + \iu y) \le s(\iu y)$.
\end{enumerate}

Given these facts, we can build a simple lower bound for $s(x + \iu y)$:
\begin{align*}
l(x + \iu y)
   &= \abs{\frac{(W^2 + 1) \sinh y - 2 W \cosh y}{(W^2 + 1) \sinh y + 2 W \cosh y}}
\\ &= \abs{\frac{\tanh y - V}{\tanh y + V}} && \text{(since $\cosh y > 0$)}
\end{align*}

It's pretty clear that $l(k)$ has a continuum of zeros over the line $\Im k = Z$, which implies that $\ln l(k)$ has continuum number of singularities over this line. Intuitively, it shouldn't spoil the convergence of integral since the contour of integration cound intersect the singularities of the original function anyway. And indeed, we will give a rigorous argument that we still can prove convergence in this case. Since the function is independent from the real part of the argument now, for brewity, we will omit it and defince $l(y) = l(\iu y)$.

Now, we will simplify the integral using the bound we just constructed:
\begin{align*}
       \int\limits_{t=0}^{2 \pi} \abs{f(t)}^2 dt
   = & \int\limits_{t = 0}^{2 \pi} \ln^2 l(R \eexp{\iu t} + \iu C) \frac{R}{\norm{R \eexp{\iu t} + \iu C + i}^2} dt
\\ = & \int\limits_{t = 0}^{2 \pi} \ln^2 l(R \sin t + C) \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dt
\end{align*}

First, notice that:

\begin{equation*}
\begin{aligned}
   \sin(-\pi/2 + t)   &= \sin(-\pi/2 - t) = - \cos t
\\ \cos^2(-\pi/2 + t) &= \cos^2(-\pi/2 = t) = \sin^2 t
\end{aligned}
\end{equation*}
, that is, the integrand is symmetric with respect to $y$ and for proving convergence it is enough to prove convergence on the (half circle) contour defined by $-\pi/2 \le t \le \pi/2$.

Next, we do a variable change:
\begin{equation*}
\begin{aligned}
   y         &= R \sin t + C
\\ t         &= \asin \frac{y - C}{R}
\\ dt        &= \frac{1}{\sqrt{R^2 - (C - y)^2}} dy
\\ \cos t    &= \frac{\sqrt{R^2 - (C - y)^2}}{R}
\\ y(-\pi/2) &= C - R 
\\ y(\pi/2)  &= C + R 
\end{aligned}
\end{equation*}
, and after substitution:
\begin{equation}\label{eq:int_f}
\resizebox{0.9\hsize}{!}{$
\begin{aligned}
    & \int\limits_{y = C - R}^{C + R} \ln^2 f(y) \frac{R}{R^2 \cos^2 t + (R \sin t + C + 1)^2} dy \\
=   & \int\limits_{y = C - R}^{C + R} \ln^2 f(y) \frac{R}{R^2 - (C - y)^2 + (y + 1)^2} \frac{1}{\sqrt{R^2 - (C - y)^2}} dy\\
=   & \int\limits_{y = C - R}^{C + R} \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}  dy\\
\end{aligned}
$}
\end{equation}

On the integration path we cross singularities at $y = C - R$, $y = Z$, $y = C + R$, and the integrand is still too complex for direct estimation. Let's split the integration path in multiple segments and estimate them independently.

\subsubsection{Case 1: $C - R \le y \le Z$}
A crucial property of $s(k)$ is its convergence to 1 as $\Im k$ goes to 0 (which is because $s$ is the determinant of S-matrix), since then $\ln s(k)$ goes to zero, which is necessary to compensate the singularity of $\frac{1}{R - C + y}$ at $y = C - R$. 
This means that to prove convergence using lower bound for $s(k)$, we have to require that $s(k)$ also converges to $1$ as $\Im k$ goes to $0$.

% TODO plot?
Since $l$ is convex when $0 \le y \le Z$, we can estimate it from below using its first derivative at $0$. However, this is not enough, since it will this will violate the property of the estimate being positive (it is under the logarithm sign), so we have to be more careful and approximate the function at $Z$ with its first derivative as well, and then glue them together at some point $Z_0$:
\begin{align*}
f(y)
& = 
\begin{cases}
l'(0) y + 1   &, 0 \le y < Z_0  \\
l'(Z) (y - Z) &, Z_0 \le y < Z \\
\end{cases}
\\
& =
\begin{cases}
\frac{-2}{V} y + 1   &, 0 \le y < Z_0  \\
\frac{1}{2 V}(V^2 - 1) (y - Z) &, Z_0 \le y < Z \\
\end{cases}
\end{align*}

Note that lower bound does not have to be a continuous function, so we can pick any number in $[C - R, Z)$ as $Z_0$. For the ease of calculations, let's take $Z_0 = \frac{V}{4}$.

Next we compute upper bounds for the integral \ref{eq:int_f} on $[C - R, \frac{V}{4})$ and $[\frac{V}{4}, Z)$ separately.

\paragraph{$C - R \le y < \frac{V}{4}$}

Note that for $C - R \le y \le \frac{V}{4}$:
\begin{align*}
       & \int \ln^2 l(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}}
\\ \le & \int \ln^2 (1 - \frac{2}{V} y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
\end{align*}

Now, we use a well known inequality which holds for $x > -1$: % REFTODO
\[
\frac{x}{1 + x} \le \ln (1 + x)
\]
, where in our case $x = -\frac{2}{V} y$. Since the expression under logarithm is less than 1, we get $\ln^2 (1 + x) \le \frac{x^2}{(1 + x)^2}$:
\begin{align*}
       & \dots 
\\ \le & \int \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V}y)^2}  \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
\\ \le & \int \frac{\frac{4}{V^2}y^2}{(1 - \frac{2}{V} \frac{V}{4})^2}  \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + y}}
\\ =   & \frac{\frac{4}{V^2}}{(1 - \frac{2}{V} \frac{V}{4})^2} \frac{R}{\sqrt{R + C - Z}}  \int \frac{y^2}{R^2 - C^2 + 2 (C + 1) y + 1}  \frac{1}{\sqrt{R - C + y}}
\end{align*}

It's clear that the multiplier before the integral has order $\mcO(\sqrt{R})$ (we can ignore the terms dependent on $V$ only since $V$ is a constant independent of $r$).

The first part of the integrand has the form $\frac{y^2}{a + b y}$, where $a = R^2 - C^2 + 1, b = 2 (C + 1)$; when $R$ and $C$ are big enough, $a > 0$ and $b > 0$. That means $\frac{y^2}{a + b y}$ will be nonnegative when $y > 0$, and non decreasing, since:
\[
  \left(\frac{y^2}{a + b y}\right)'
= \frac{2y}{a + by} + y^2 \frac{-b}{(a + by)^2}
= \frac{2y (a + by) - b y^2}{(a + by)^2}
= \frac{y (2a + by)}{(a + by)^2}
\ge 0
\]

This implies that we can estimate the function from above by using its value on the rightmost point of the interval at $\frac{V}{4}$.
\[
\frac{y^2}{a + b y} \le \frac{\frac{V^2}{16}}{R^2 - C^2 + 1 + 2 (C + 1) \frac{V}{4}} = \mcO\left(\frac{1}{R}\right)
\]

Interal of the second part of the integrand is:
\[
\int\limits_{C - R}^{\frac{V}{4}} \frac{1}{\sqrt{R - C + y}} = 2 \sqrt{\frac{V}{4} - (C - R)} < 2 \sqrt{\frac{V}{4}} = \mcO(1)
\]

And finally, after combining we get $\mcO(\sqrt{R}) \mcO\left(\frac{1}{R}\right) \mcO(1)  = \mcO\left(\frac{1}{\sqrt{R}}\right)$.

\paragraph{$\frac{V}{4} \le y < Z$}
